Yeast RNA-seq 48 sample simulation study

### 2018-07-25 datasets/RNA-Seq/polyester-simulation.Rmd
Fix typo introduced in previous commit
Make weighting scheme the same in informative and uninformative sims

  # DE simulation
  if(nDE > 0){
    wts <- rep(1, nrow(dds_test))
    if(!uninformativeCovariate)
      wts <- log10(rowMeans(counts)+1)

    DE <- sample(1:nrow(dat_alt), nDE, prob = wts)
    truth[DE] <- TRUE

>>>>

  # DE simulation
  if(nDE > 0){
    wts <- log10(rowMeans(dat_alt)+1)
    DE <- sample(1:nrow(dat_alt), nDE, prob = wts)
    truth[DE] <- TRUE

### 2018-07-25 datasets/RNA-Seq/yeast-simulation.Rmd
Make weighting scheme the same in informative and uninformative sims

  if(nDE > 0){
    # pick random set of nDE genes to add signal to
    wts <- rep(1, nrow(dds_test))
    if(!uninformativeCovariate)
      wts <- log10(rowMeans(counts(dds_test, normalize = TRUE))+1)
    DE <- sample(1:nrow(dds_test), nDE, prob = wts)
    truth[DE] <- TRUE

>>>>

  if(nDE > 0){
    # pick random set of nDE genes to add signal to
    wts <- log10(rowMeans(counts(dds_test, normalize = TRUE))+1)
    DE <- sample(1:nrow(dds_test), nDE, prob = wts)
    truth[DE] <- TRUE
